\Rpackage{MSnbase}: labelled MS2 data pre-processing, visualisation and quantification.

### 2012-05-31 inst/doc/MSnbase-demo/MSnbase-demo.Rnw
CHANGES IN VERSION 1.5.8 -------------------------  o added aa data in environment data.frame <2012-05-22 Tue>  o fixed MSnbase:::subsetBy (used by topN) when    ncol(object) == 1 <2012-05-25 Fri>  o new nQuants function <2012-05-31 Thu>  o minor vignettes updates <2012-05-31 Thu>
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MSnbase@66318 bc3139a8-67e5-0310-9ffc-ced21a209358

<<make2exps1, echo=TRUE, cache=FALSE>>=
exp1 <- quantify(itraqdata, reporters = iTRAQ4, verbose = FALSE)
sampleNames(exp1)
exp2 <- quantify(rawdata, reporters = iTRAQ4, verbose = FALSE)
sampleNames(exp2)
@

@@

<<make2exps2, echo=TRUE, cache=FALSE>>=
set.seed(1)
i <- sample(length(itraqdata), 35)
j <- sample(length(itraqdata), 35)
exp1 <- quantify(itraqdata[i], reporters = iTRAQ4, verbose = FALSE)
exp2 <- quantify(itraqdata[j], reporters = iTRAQ4, verbose = FALSE)
table(featureNames(exp1) %in% featureNames(exp2))
exp1 <- combineFeatures(exp1, groupBy = fData(exp1)$ProteinAccession)
exp2 <- combineFeatures(exp2, groupBy = fData(exp2)$ProteinAccession)
head(featureNames(exp1))
featureNames(exp1) <- fData(exp1)$ProteinAccession
featureNames(exp2) <- fData(exp2)$ProteinAccession
head(featureNames(exp1))
@

>>>>

<<makeexp12, echo=TRUE, cache=FALSE>>=
exp1 <- quantify(itraqdata, reporters = iTRAQ4,
                 parallel = FALSE, verbose = FALSE)
sampleNames(exp1)
exp2 <- quantify(rawdata, reporters = iTRAQ4,
                 parallel = FALSE, verbose = FALSE)
sampleNames(exp2)
@

@@

<<make2exps2, echo=TRUE, cache=FALSE>>=
set.seed(1)
i <- sample(length(itraqdata), 35)
j <- sample(length(itraqdata), 35)
exp1 <- quantify(itraqdata[i], reporters = iTRAQ4,
                 parallel = FALSE, verbose = FALSE)
exp2 <- quantify(itraqdata[j], reporters = iTRAQ4,
                 parallel = FALSE, verbose = FALSE)
table(featureNames(exp1) %in% featureNames(exp2))
exp1 <- combineFeatures(exp1,
                        groupBy = fData(exp1)$ProteinAccession)
exp2 <- combineFeatures(exp2,
                        groupBy = fData(exp2)$ProteinAccession)
head(featureNames(exp1))
featureNames(exp1) <- fData(exp1)$ProteinAccession
featureNames(exp2) <- fData(exp2)$ProteinAccession
head(featureNames(exp1))
@
